**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-05-24 Manuscripts/Manuscript by chapters -v1/Full_document.Rmd
Updated manuscript

library(patchwork)
library(tidyverse)
library(mvnfast)
library(nlme)
library(ggsci)
library(mgcv)
library(gratia)
library(ghibli)
library(viridis)
set.seed(1) #set seed for reproducibility

>>>>

library(patchwork)
library(tidyverse)
library(mvnfast)
library(nlme)
library(mgcv)
library(gratia)
library(viridis)
set.seed(1) #set seed for reproducibility
